Contrast\_Writeup

### 2019-03-08 R Files/Updated Model/Contrast_Writeup.tex
Re-re-fit the contrast model and began writeup

---
title: "Contrast_Writeup"
author: "Aidan Mullan"
date: "3/7/2019"
header-includes:
  - \usepackage{float}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.pos = 'htb!')
```

## Contrast Distributions

@@

```{r, fig.height = 5, fig.width = 10}
PE_raw <- read.csv("Data/1st_Set/PE_clean.csv")
PE_short <- PE_raw[,c(4,5,7,8,9,10,11,12)]
PE_chest <- subset(PE_short, subset = Procedure == "Chest Only")
index <- which(PE_chest$Contrast.Given > 150)
PE <- na.omit(PE_chest[-index,])

age_cuts <- c("<20", "20-30", "30-40", "40-50","50-60", "60-70",
              "70-80", "80-90", ">90")
PE$Age10 <- cut(PE$Age, breaks = c(-1,seq(20,90,10), 110), labels = age_cuts)
BMI_cuts <- c("10-15", "15-20", "20-25", "25-30","30-35", "35-40",
              "40-45", "45-50", "50-55", ">55")
PE$BMI10 <- cut(PE$BMI, breaks = c(seq(10,55,5),92), labels = BMI_cuts)

par(mfrow = c(1,2))
contrast_by_age <- tapply(PE$Contrast.Given, PE$Age10, "mean")
plot(contrast_by_age, type = "l", ylab = "Contrast Given", xlab = "Age Group", xaxt = "n",
     main = "Figure 1b: Mean Contrast Administered by Age", cex.main = 1, yaxt = "n", ylim = c(70,95))
points(contrast_by_age)
axis(1, at = 1:9, labels = age_cuts, cex.axis = .7, mgp = c(3,0.5,0))
axis(2, at = seq(70,95,5))

contrast_by_bmi <- tapply(PE$Contrast.Given, PE$BMI10, "mean")
plot(contrast_by_bmi, type = "l", ylab = "Contrast Given", xlab = "BMI Group", xaxt = "n",
     main = "Figure 1b: Mean Contrast Administered by BMI", cex.main = 1, yaxt = "n")
points(contrast_by_bmi)
axis(1, at = 1:10, labels = BMI_cuts, cex.axis = .7, mgp = c(3,0.5,0))
axis(2, at = seq(70,120,10))
par(mfrow = c(1,1))
```

@@

```{r, fig.height = 5, fig.width = 8}
par(mar = c(5,5,3,5))
bmi_by_age <- tapply(PE$BMI, PE$Age10, "mean")
plot(contrast_by_age, type = "l", ylab = "Contrast Given", xlab = "Age Group", xaxt = "n",
     main = "Figure 2: Mean BMI and Contrast Administered by Age", cex.main = 1, yaxt = "n", ylim = c(70,95))
points(contrast_by_age)
axis(1, at = 1:9, labels = age_cuts, cex.axis = .7, mgp = c(3,0.5,0))
axis(2, at = seq(70,95,5))
par(new = T)
plot(bmi_by_age, type = "l", axes = F, lty = 2, xlab = NA, ylab = NA, col = "red")
points(bmi_by_age, col = "red", pch = 16)
axis(side = 4)
mtext(side = 4, line = 3, "BMI")
legend("topright", legend = c("Contrast", "BMI"), lty = c(1,2), col = c("black", "red"))
```

## Contrast Model

 Then, a linear model was fit for contrast considering age (<18, 18-35, >35), BMI (<20, 20-40, >40), Gender, Location of Admission, and Type of CT scanner used. Model coefficients are given in Table 1.

@@

#### Influence of Scanner Type

Our contrast model found a significant effect for the type of scanner used. Post-hoc comparisons conducted using Tukey's HSD found that the DS scanners were associated with significantly lower levels of contrast than all 3 other scanners ($p<.001$ for all 3). Additionally, the 64SSwIR and 64SSwoIR scanners had significantly higher levels of contrast than the 128SSwIR scanner (64SSwIR: $p = .001$; 64SSwoIR: $p = .016$). There was no significant difference in contrast usage between the 64SSwIR and 64SSwoIR scanners.

From the model, these significant differences can be interpreted as:
\begin{itemize}
\item On average, patients who receive a CT using the DS scanner are administered 9.32cc less contrast than patients on the 128SSwIR scanner, 14.09cc less contrast than patients on the 64SSwIR scanner, and 15.07cc less contrast than patients on the 64SSwoIR scanner
\item On average, patients who receive a CT using the 128SSwIR scanner are administered 4.77cc less contrast than patients on the 64SSwIR scanner and 5.75cc less contrast than patients on the 64SSwoIR scanner.
\end{itemize}

## Radiation and Age

In earlier write-ups, we have seen a quadratic relationship between radiation administered and patient age. There appears to be a peak in effective dosage that occurs somewhere between 30 and 60 years of age. To better pinpoint exactly where this peak occurs, we first subset the data to patients between 25 and 65 years of age. We then create age groups at five-year intervals and retrieve the mean effective dose for each group. These results are given in Figure 3.

```{r}
PE_midage <- subset(PE, subset = Age > 25 & Age < 65)
PE_midage$Age2 <- cut(PE_midage$Age, breaks = seq(25,65,5), labels = seq(30,65,5))
rad_by_age2 <- tapply(PE_midage$Eff.Dose, PE_midage$Age2, "mean")
```

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Contrast\_Writeup},
            pdfauthor={Aidan Mullan},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Contrast\_Writeup}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Aidan Mullan}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{3/7/2019}

\usepackage{float}

\begin{document}
\maketitle

\subsection{Contrast Distributions}\label{contrast-distributions}

@@

\includegraphics{Contrast_Writeup_files/figure-latex/unnamed-chunk-1-1.pdf}

@@

\includegraphics{Contrast_Writeup_files/figure-latex/unnamed-chunk-2-1.pdf}

\subsection{Contrast Model}\label{contrast-model}

Then, a linear model was fit for contrast considering age
(\textless{}18, 18-35, \textgreater{}35), BMI (\textless{}20, 20-40,
\textgreater{}40), Gender, Location of Admission, and Type of CT scanner
used. Model coefficients are given in Table 1.

@@

\paragraph{Influence of Scanner Type}\label{influence-of-scanner-type}

Our contrast model found a significant effect for the type of scanner
used. Post-hoc comparisons conducted using Tukey's HSD found that the DS
scanners were associated with significantly lower levels of contrast
than all 3 other scanners (\(p<.001\) for all 3). Additionally, the
64SSwIR and 64SSwoIR scanners had significantly higher levels of
contrast than the 128SSwIR scanner (64SSwIR: \(p = .001\); 64SSwoIR:
\(p = .016\)). There was no significant difference in contrast usage
between the 64SSwIR and 64SSwoIR scanners.

From the model, these significant differences can be interpreted as:

\begin{itemize}
\item On average, patients who receive a CT using the DS scanner are administered 9.32cc less contrast than patients on the 128SSwIR scanner, 14.09cc less contrast than patients on the 64SSwIR scanner, and 15.07cc less contrast than patients on the 64SSwoIR scanner
\item On average, patients who receive a CT using the 128SSwIR scanner are administered 4.77cc less contrast than patients on the 64SSwIR scanner and 5.75cc less contrast than patients on the 64SSwoIR scanner.
\end{itemize}

\end{document}
